Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-09-14 ms.tex
per referee suggestion, mention Figure 7 of 2011 Planck team dust paper
thank refere
corrected typo in beta threshold in section 9

To assess the accuracy of low-frequency emission predictions, we compare the 
observed \PLANCK~HFI map at each of 100, 143, 217 GHz to the corresponding 
single-MBB and two-component predictions, with all maps smoothed to $1^{\circ}$
FWHM and binned down to $N_{side}$=$64$. We restrict to the same set of pixels 
used for the goodness-of-fit analysis of $\S$\ref{sec:hier}, with 
$|b|>30^{\circ}$ and $|\beta|>30^{\circ}$, also avoiding molecular emission, 
the SMICA inpainting mask, and compact sources. We then perform a linear fit 
between the \PLANCK~observed emission and the predicted emission at each 
frequency and for each emission model. For these fits, we consider the 
predicted emission to be the independent variable, since it has higher S/N than
the observations, especially at 100 and 143 GHz. We also assign pixel weights 
proportional to the predicted emission, so that the best-fit lines faithfully 
capture the linear trend exhibited without being biased by the large number of 
very low S/N pixels with minimal emission. Scatter plots between the predicted 
and observed emission are shown in Figure \ref{fig:lofreq}. The best-fit lines 
are overplotted and their equations are given in the top left corner of each 
subplot.

In both the single-MBB and two-component cases, all of the best fit offsets are
within the uncertainties quoted in Table \ref{table:offs}. On the other hand, 
the top row of Figure \ref{fig:lofreq} shows that the \cite{planckdust} 
single-MBB predictions yield slopes substantially different from unity: 1.079 
at 217 GHz, 1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes 
are larger than unity indicates that the \cite{planckdust} predictions are 
systematically low. The systematic underprediction evidently becomes gradually 
more pronounced as lower frequencies are considered, with a 7.9\% 
underprediction at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% 
underprediction at 100 GHz.

@@

This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No. DGE1144152. We acknowledge support
of NASA grant NNX12AE08G for this research. Based on observations obtained with
Planck (http://www.esa.int/Planck), an ESA science mission with instruments and
contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}

>>>>

To assess the accuracy of low-frequency emission predictions, we compare the 
observed \PLANCK~HFI map at each of 100, 143, 217 GHz to the corresponding 
single-MBB and two-component predictions, with all maps smoothed to $1^{\circ}$
FWHM and binned down to $N_{side}$=$64$. We restrict to the same set of pixels 
used for the goodness-of-fit analysis of $\S$\ref{sec:hier}, with 
$|b|>30^{\circ}$ and $|\beta|>10^{\circ}$, also avoiding molecular emission, 
the SMICA inpainting mask, and compact sources. We then perform a linear fit 
between the \PLANCK~observed emission and the predicted emission at each 
frequency and for each emission model. For these fits, we consider the 
predicted emission to be the independent variable, since it has higher S/N than
the observations, especially at 100 and 143 GHz. We also assign pixel weights 
proportional to the predicted emission, so that the best-fit lines faithfully 
capture the linear trend exhibited without being biased by the large number of 
very low S/N pixels with minimal emission. Scatter plots between the predicted 
and observed emission are shown in Figure \ref{fig:lofreq}. The best-fit lines 
are overplotted and their equations are given in the top left corner of each 
subplot.

In both the single-MBB and two-component cases, all of the best fit offsets are
within the uncertainties quoted in Table \ref{table:offs}. On the other hand, 
the top row of Figure \ref{fig:lofreq} shows that the \cite{planckdust} 
single-MBB predictions yield slopes substantially different from unity: 1.079 
at 217 GHz, 1.126 at 143 GHz, and 1.188 at 100 GHz. The fact that the slopes 
are larger than unity indicates that the \cite{planckdust} predictions are 
systematically low. The systematic underprediction evidently becomes gradually 
more pronounced as lower frequencies are considered, with a 7.9\% 
underprediction at 217 GHz, a 12.6\% underprediction at 143 GHz and an 18.8\% 
underprediction at 100 GHz. A deficit in single-MBB predictions relative to
the observed \PLANCK~100-217 GHz emission was also noted in 
\cite{planckdust2011}, e.g. their Figure 7.

@@

We would like to thank the anonymous referee for their helpful suggestions. 
This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No. DGE1144152. We acknowledge support
of NASA grant NNX12AE08G for this research. Based on observations obtained with
Planck (http://www.esa.int/Planck), an ESA science mission with instruments and
contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}
